\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[margin=1.27cm]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{array}

% Remove page numbers
\pagestyle{empty}

% Custom section formatting
\titleformat{\section}{\normalfont\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{16pt}{8pt}

% Remove paragraph indentation
\setlength{\parindent}{0pt}

\begin{document}

%----------HEADING-----------------
{\fontsize{26}{32}\selectfont \textbf{Ahmad Jalil}} 

\vspace{6pt}

{\fontsize{14}{16}\selectfont me@ahmadjalil.com | (778) 267-9144 | Prince George, BC | ahmadjalil.com} 

\vspace{-4pt}

\noindent\rule{\textwidth}{0.4pt}

\vspace{-4pt}

%-----------EXPERIENCE-----------------
\section{Experience}

\vspace{4pt}

\noindent\textbf{Northern Analytical Laboratory Services} \hfill November 2020 – Present \\
\textit{Research Assistant} | \textit{September 2022 – Present} \hfill Prince George, BC
\begin{itemize}[leftmargin=*, topsep=2pt, itemsep=1pt, parsep=0pt]
\item Work both independently and in a team in a laboratory environment, performing tasks that involve collection and processing of samples using various instruments while maintaining and calibrating them
\item Revamped invoicing system to automate payment tracking processes, reducing customer inquiries and improving overall customer satisfaction.
\item Streamlined and optimized laboratory workflow by implementing new methods and protocols, resulting in an increase in sample processing efficiency.
\item Authored and disseminated scientific papers and reports, contributing to the lab's knowledge base.
\end{itemize}

\vspace{1pt}
\textit{Student Research Assistant} | \textit{November 2020 – September 2022}
\begin{itemize}[leftmargin=*, topsep=2pt, itemsep=1pt, parsep=0pt]
\item Organize, review, and correct research data, creating illustrative graphs and charts for reports
\item Process data using statistical software including Excel, Prism, and Rstudio, to facilitate thorough data analysis
\item Apply graphic design skills (Photoshop, Illustrator, InDesign) to create various materials for the Northern Analytical Laboratory Services
\end{itemize}

\vspace{8pt}

\noindent\textbf{Relentless Pursuit Ventures} \hfill May 2024 – August 2024 \\
\textit{Health Technology Research Analyst (Intern)} \hfill Remote
\begin{itemize}[leftmargin=*, topsep=2pt, itemsep=1pt, parsep=0pt]
\item Conducted comprehensive research on health technology innovations for seniors in rural and remote communities across Canada.
\item Identified and analyzed key stakeholders in the age-tech and healthcare sectors, including government agencies, healthcare providers, technology companies, and advocacy groups.
\end{itemize}

\vspace{8pt}

\noindent\textbf{Northern Health} \hfill May 2024 – Present \\
\textit{Informatics Specialists} | \textit{December 2024 – Present} \hfill Prince George, BC
\begin{itemize}[leftmargin=*, topsep=2pt, itemsep=1pt, parsep=0pt]
\item Led the integration and optimization of health information technologies, improving access to patient/client information and enhancing evidence-based practices across Northern Health regions.
\item Collaborated with clinical leaders, HIM leaders, and physicians to align healthcare systems with operational needs, while designing and maintaining health information management content.
\item Directed change initiatives and provided leadership in recruiting, coaching, and evaluating staff, fostering innovation and supporting the adoption of international coding standards.
\end{itemize}

\vspace{1pt}
\textit{PICS Intern} | \textit{May 2024 – December 2024}
\begin{itemize}[leftmargin=*, topsep=2pt, itemsep=1pt, parsep=0pt]
\item Utilize Geographic Information Systems (GIS) software to analyze and map data relevant to public health concerns across Northern Health regions.
\item Created and presented comprehensive GIS-based reports to high-level decision-makers to support informed decision-making on public health concerns.
\item Developed a standardized database to track and analyze provincial-wide systems, enhancing data consistency and accessibility across Northern Health regions.
\end{itemize}

\vspace{8pt}

\noindent\textbf{University of Northern British Columbia} \hfill January 2024 – December 2024 \\
\textit{Teaching Assistant} \hfill Prince George, BC
\begin{itemize}[leftmargin=*, topsep=2pt, itemsep=1pt, parsep=0pt]
\item Contributed to the creation of an online resource hub for nutrition students, providing access to lecture notes, study guides, and additional learning materials.
\end{itemize}

%-----------VOLUNTEER-----------------
\section{Volunteer}

\vspace{4pt}

\noindent\textbf{St. Vincent De Paul} \hfill December 2020 – Present \\
\textit{Service Volunteer} \hfill Prince George, BC
\begin{itemize}[leftmargin=*, topsep=2pt, itemsep=1pt, parsep=0pt]
\item Prepared and served meals to those in need, promoted community wellness, and efficiently managed the distribution of donated goods.
\end{itemize}

\vspace{8pt}

\noindent\textbf{Rural eMentoring BC} \hfill September 2020 – Present \\
\textit{Highschool Mentor} \hfill Remote
\begin{itemize}[leftmargin=*, topsep=2pt, itemsep=1pt, parsep=0pt]
\item Cultivated a confidential, supportive mentorship with a high school mentee, providing guidance on personal and academic challenges to foster personal and educational development.
\end{itemize}

\vspace{8pt}

\noindent\textbf{Over The Edge Newspaper Society} \hfill March 2024 – Present \\
\textit{Acting Editor-in-Chief} \hfill Prince George, BC
\begin{itemize}[leftmargin=*, topsep=2pt, itemsep=1pt, parsep=0pt]
\item Negotiated a printing deal with the main newsprint supplier in Prince George, securing the production of 22,000 copies per issue.
\item Redesigned the newspaper's logo and brand image to modernize and align with current media trends.
\item Conducted audience research to identify preferences and tailored content to increase engagement.
\item Centralized information structures to streamline communication and enhance workflow efficiency.
\end{itemize}

\vspace{8pt}

\noindent\textbf{Sparklab} \hfill September 2023 – Present \\
\textit{Technical Analyst} \hfill Prince George, BC
\begin{itemize}[leftmargin=*, topsep=2pt, itemsep=1pt, parsep=0pt]
\item Engage with researchers to understand their specific needs and challenges in laboratory and field environments.
\item Design customized solutions using CAD (Computer-Aided Design) software to address the unique requirements of various research projects.
\end{itemize}

\vspace{8pt}

\noindent\textbf{University of Northern British Columbia} \hfill September 2022 – Present \\
\textit{Research Ambassador} \hfill Prince George, BC
\begin{itemize}[leftmargin=*, topsep=2pt, itemsep=1pt, parsep=0pt]
\item Act as a primary liaison between students and the research community at UNBC, promoting engagement and participation in research activities.
\item Organize and lead informational sessions and workshops to educate students about the research process, opportunities, and the significance of research contributions.
\end{itemize}

\vspace{8pt}

\noindent\textbf{Northern Health} \hfill April 2023 – Present \\
\textit{Activity Volunteer} \hfill Prince George, BC
\begin{itemize}[leftmargin=*, topsep=2pt, itemsep=1pt, parsep=0pt]
\item Assist recreation therapists and engage in activities with residents at Rainbow Lodge \& Gateway, a long-term care home and facilities, enhancing their daily lives and well-being.
\item Provide emotional support and reassurance to dementia patients, helping them feel more secure and oriented in their environment.
\item Deepen my understanding of patient-centered medicine through direct interactions, learning about residents' needs and perspectives.
\end{itemize}

%-----------EDUCATION-----------------
\section{Education}

\vspace{4pt}

\noindent\textbf{University of Northern British Columbia} \hfill September, 2026 \\
\textit{P.hD, Natural Resources and Environmental Studies} \hfill Prince George, BC
\begin{itemize}[leftmargin=*, topsep=2pt, itemsep=1pt, parsep=0pt]
\item Focus on air quality and environmental health
\end{itemize}

\vspace{8pt}

\noindent\textbf{University of Northern British Columbia} \hfill September, 2023 – August 2024 \\
\textit{M.Sc., Natural Resources and Environmental Studies} \hfill Prince George, BC
\begin{itemize}[leftmargin=*, topsep=2pt, itemsep=1pt, parsep=0pt]
\item Focus on air quality and environmental health
\item Continued to PhD
\end{itemize}

\vspace{8pt}

\noindent\textbf{University of Northern British Columbia} \hfill May, 2023 \\
\textit{B.HSc., Biomedical Studies (Honours)} \hfill Prince George, BC
\begin{itemize}[leftmargin=*, topsep=2pt, itemsep=1pt, parsep=0pt]
\item Minor: Natural Resource Planning and Operations (Forestry).
\item The Lieutenant Governor's Medal for Inclusion, Democracy and Reconciliation.
\end{itemize}

%-----------PROFESSIONAL DEVELOPMENT-----------------
\section{Professional Development}

\vspace{4pt}

\noindent\textbf{Mohawk College} \hfill March, 2024 \\
\textit{Digital Twins - Fundamentals, Techniques \& Approaches} \hfill Remote

\vspace{8pt}

\noindent\textbf{British Columbia Institute of Technology} \hfill May, 2023 \\
\textit{Applied Internet of Things (IoT)} \hfill Vancouver, BC

\vspace{8pt}

\noindent\textbf{Holland College} \hfill June, 2022 \\
\textit{Building Envelope Science} \hfill Remote

\vspace{8pt}

\noindent\textbf{John Hopkins University} \hfill December, 2021 \\
\textit{Covid-19 Contact Tracer} \hfill Remote

%-----------CERTIFICATIONS & SKILLS-----------------
\section{Certifications \& Skills}

\vspace{4pt}

\begin{itemize}[leftmargin=*, topsep=2pt, itemsep=1pt, parsep=0pt]
\item \textbf{Certifications:} OFA Level 1; TCPS 2; Environmental Professional in Training (EPt)
\item \textbf{Skills:} Power BI; Research Skills; GIS; R Studio; Brand Identity Maps; Analytical Nature; Adobe Suite; Business Process Reengineering; SPSS; logistics; Fluent in Arabic; Powerful Decision-Making Expertise; Grant Proposal
\end{itemize}

%-----------AWARDS-----------------
\section{Awards}

\vspace{4pt}

\noindent\textbf{Canada Graduate Scholarships – Michael Smith Foreign Study Supplements} \\
\textit{Canadian Institutes of Health Research} \hfill January 2025 \\
The Government of Canada launched this program in 2008 to support high-calibre graduate students in building global linkages and international networks through the pursuit of exceptional research experiences at research institutions outside of Canada. By accessing international scientific research and training, CGS-MSFSS recipients will contribute to strengthening the potential for collaboration between Canadian and international universities and affiliated research institutions.

\vspace{8pt}

\noindent\textbf{Canada Graduate Scholarships} \\
\textit{Canadian Institutes of Health Research} \hfill April 2024 \\
The Canada Graduate Scholarships is designed to enhance the research skills and training of highly qualified personnel in health, natural sciences, engineering, and social sciences. This prestigious program is jointly administered by Canada's three granting agencies: CIHR, NSERC, and SSHRC, supporting students annually across all disciplines. The program selects scholars through a rigorous evaluation of their academic excellence, research potential, and personal competencies.

\vspace{8pt}

\noindent\textbf{British Columbia Graduate Scholarship} \\
\textit{The Ministry of Advanced Education, Skills and Training} \hfill April 2024 \\
The British Columbia Graduate Scholarship supports exceptional students at public post-secondary institutions across the province, with a focus on STEM and professional fields. Valued at \$17,500 the scholarships are merit-based and aim to attract top talent who contribute significantly to their disciplines. This initiative helps reduce financial barriers and promote educational innovation in British Columbia.

\vspace{8pt}

\noindent\textbf{Lieutenant-Governor's Medal for Inclusion, Democracy and Reconciliation} \\
\textit{Lieutenant Governor of British Columbia} \hfill May 2023 \\
The Lieutenant-governor's Medal for Inclusion, Democracy and Reconciliation recognizes outstanding contributions from UNBC's graduating class of over 700 students to promoting inclusion, democracy, and reconciliation within the UNBC community. The award recognizes exceptional leadership, advocacy, and commitment to creating a more inclusive and equitable campus environment.

\vspace{8pt}

\noindent\textbf{Undergraduate Student Research Award} \\
\textit{Natural Sciences and Engineering Research Council of Canada} \hfill April 2023 \\
Natural Sciences and Engineering Research Council of Canada Undergraduate Student Research Award, awarded for outstanding research contributions in the natural sciences and engineering fields. The award recognizes exceptional research skills, creativity, and potential for future contributions to the field.

\vspace{8pt}

\noindent\textbf{BC Northern Real Estate Board Award} \\
\textit{BC Northern Real Estate Board} \hfill August 2021 \\
The award is for recipients whose home town must be within the geographical boundaries defined by the Yukon border to the north, 70 Mile House to the south, Haida Gwaii Islands to the west, and the Alberta border to the east, including the communities of Dawson Creek, Chetwynd, and Tumbler Ridge. Meeting the criteria for good academic standing is the primary basis for selection.

\vspace{8pt}

\noindent\textbf{Governor General's Academic Medal} \\
\textit{The Governor General of Canada} \hfill July 2018 \\
I was awarded the Governor General's Academic Medal in recognition of my outstanding academic achievement. This prestigious award is given to the student with the highest academic standing in their graduating class. I received this honor for achieving the highest overall average in my school, demonstrating exceptional dedication and excellence in my studies. The Governor General's Academic Medal is a national recognition of academic excellence and is highly regarded in the academic community.

%-----------PRESENTATIONS-----------------
\section{Presentations}

\vspace{4pt}

\noindent\textbf{Assessing the health impacts of particulate bound metals in downtown Prince George: A health indexing study on the differential effects of high and low dust days} \\
\textit{Cascadia Symposium on Environmental, Occupational, and Population Health 2024} \hfill Blaine, WA

\vspace{8pt}

\noindent\textbf{Particulate Matter-Bound Metals as an Assessment of Air Pollution in the City of Prince George} \\
\textit{UNBC Research Week 2023} \hfill Prince George, BC

\vspace{8pt}

\noindent\textbf{Heavy metals and polycyclic aromatic hydrocarbons in ambient air during episodes of springtime road dust} \\
\textit{UNBC Research Week 2021} \hfill Prince George, BC

%-----------PUBLICATIONS-----------------
\section{Publications}

\vspace{4pt}

Eric S. Coker, Nikita Saha Turna, Mya Schouwenburg, Ahmad Jalil, Charles Bradshaw, Michael Kuo, Molly Mastel, Hossein Kazemian, Meghan Roushorne \& Sarah B. Henderson. (2023). \textbf{Characterization of the short-term temporal variability of road dust chemical mixtures and meteorological profiles in a near-road urban site in British Columbia}. \textit{Journal of the Air \& Waste Management Association}. 73(6): 502-516.

\end{document}